---
title: "My submission document"
author: "Neustc"
date: "`r Sys.Date()`"
output: 
 html_document: 
   keep_md: yes
   theme: cerulean
   highlight: kate
   fig_width: 6
   fig_height: 6
   toc: yes
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


## Text
This is an Rmarkdown document for my submission. I used two dataset. The cars dataset [https://stat.ethz.ch/R-manual/R-patched/library/datasets/html/cars.html](https://stat.ethz.ch/R-manual/R-patched/library/datasets/html/cars.html) and the pressure dataset [https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/pressure.html](https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/pressure.html). In this document we will see an example of a bulleted list of 3 items, a plot of the pressure dataset and a table of the tops 6 rows of the cars dataset



## bulleted list of 3 or more items 

* abstract
* pressure
* cars


## A plot of the built-in 'pressure' dataset


```{r pressure, echo=FALSE}
plot(pressure)
```


## A table of the top 6 rows of the built-in 'cars' dataset
table (cars)

```{r echo=FALSE} 
knitr::kable(head(cars))
```

